---
title: "Macro Data"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
    theme: default
runtime: shiny

---

```{r setup, include=FALSE}
library(flexdashboard)
library(ggplot2)
library(tidyverse)
library(rdbnomics)
library(lubridate)


setwd("C:/Users/yosty/Desktop/Desktop_Folder/14 - git/RA_primer/shiny")
source(file = "utilities_shiny.R")


```

```{r loadData}

mcl = read.csv("weoCountries.csv")

# get data from dbnomics
dataset = "WEO:2021-10"
dim = rdbnomics::rdb_dimensions(provider_code = "IMF", dataset_code = dataset)
countries = dim$IMF$`WEO:2021-10`$`weo-country`
series = unique(dim$IMF$`WEO:2021-10`$`weo-subject`)


```



Column {.sidebar}
=====================================

```{r sidebar}
selectInput(inputId="countryName",
            label="Select Country",
            choices=mcl$WEO.Country)

numericInput(inputId="xInterval", 
             label=("X Axis Interval"), 
             value=5)

numericInput(inputId="startYear", 
             label=("End Year"), 
             value=2000)

numericInput(inputId="endYear", 
             label=("Start Year"), 
             value=2020)
               

# load data from inputs
weoCode <- reactive({ mcl %>% filter(WEO.Country == input$countryName) %>% select(weo.country) %>% pull(weo.country)})
data <- reactive({read.csv(file=paste("data/", weoCode(), ".csv", sep="")) %>%
    mutate(period = year(period)) %>%
    filter(period >= input$startYear,
           period <= input$endYear)})
  


```

Gross Domestic Product {data-navmenu="Pages"}
=====================================

Column {data-width=500}
-----------------------------------------------------------------------

### Real GDP Percent Change

```{r}

renderPlot({make_line(data(), 
                      series="NGDP_RPCH", 
                      title="", 
                      subtitle="", 
                      xInterval=input$xInterval)})


```


### Gross Domestic Product, Contstant Price Local Currency - millions?

```{r}

renderPlot({make_line(data(), 
                      series="NGDP_R", 
                      title="", 
                      subtitle="", 
                      xInterval=input$xInterval)})


```

Column {data-width=500}
-----------------------------------------------------------------------


### Gross Domestic Product, Per Capita Nominal USD

```{r}

renderPlot({make_line(data(), 
                      series="NGDPDPC", 
                      title="", 
                      subtitle="", 
                      xInterval=input$xInterval)})


```

###  Output Gap, percent of potential GDP

```{r}

renderPlot({make_line(data(), 
                      series="NGAP_NPGDP", 
                      title="", 
                      subtitle="", 
                      xInterval=input$xInterval)})


```



Fiscal {data-navmenu="Pages"}
=====================================

Column {data-width=500}
-----------------------------------------------------------------------

### General Government Net Lending/Borrowing, percent of GDP

```{r}

renderPlot({make_line(data(), 
                      series="GGXONLB_NGDP", 
                      title="", 
                      subtitle="", 
                      xInterval=input$xInterval)})


```


### General Government Revenue, percent of GDP

```{r}

renderPlot({make_line(data(), 
                      series="GGR_NGDP", 
                      title="", 
                      subtitle="", 
                      xInterval=input$xInterval)})


```

Column {data-width=500}
-----------------------------------------------------------------------


### General Government Gross Debt, percent of GDP

```{r}

renderPlot({make_line(data(), 
                      series="GGXWDG_NGDP", 
                      title="", 
                      subtitle="", 
                      xInterval=input$xInterval)})


```

### General Government Expenditure, percent of GDP

```{r}

renderPlot({make_line(data(), 
                      series="GGX_NGDP", 
                      title="", 
                      subtitle="", 
                      xInterval=input$xInterval)})


```

Monetary {data-navmenu="Pages"}
=====================================

Column {data-width=500}
-----------------------------------------------------------------------

### Inflation, average consumer prices index 

```{r}

renderPlot({make_line(data(), 
                      series="PCPI", 
                      title="", 
                      subtitle="", 
                      xInterval=input$xInterval)})


```


### Implied PPP conversion rate Local currency per international dollar

```{r}

renderPlot({make_line(data(), 
                      series="PPPEX", 
                      title="", 
                      subtitle="", 
                      xInterval=input$xInterval)})


```

Column {data-width=500}
-----------------------------------------------------------------------


### Inflation, average consumer prices index percent change

```{r}

renderPlot({make_line(data(), 
                      series="PCPIPCH", 
                      title="", 
                      subtitle="", 
                      xInterval=input$xInterval)})


```

###  Gross Domestic Product, Deflator

```{r}

renderPlot({make_line(data(), 
                      series="NGDP_D", 
                      title="", 
                      subtitle="", 
                      xInterval=input$xInterval)})


```


Labor {data-navmenu="Pages"}
=====================================

Column {data-width=500}
-----------------------------------------------------------------------

### Population, scale?

```{r}

renderPlot({make_line(data(), 
                      series="LP", 
                      title="", 
                      subtitle="", 
                      xInterval=input$xInterval)})


```


### 

```{r}

renderPlot({make_line(data(), 
                      series="", 
                      title="", 
                      subtitle="", 
                      xInterval=input$xInterval)})


```

Column {data-width=500}
-----------------------------------------------------------------------


### Unemployment

```{r}

renderPlot({make_line(data(), 
                      series="LUR", 
                      title="", 
                      subtitle="", 
                      xInterval=input$xInterval)})


```

###  

```{r}

renderPlot({make_line(data(), 
                      series="", 
                      title="", 
                      subtitle="", 
                      xInterval=input$xInterval)})


```




